Performance of two different ontological and data access methods

### 2014-07-03 cold2014/magnus.tex
small fixes in spacing
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@723 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{wraptable}{r}{0.35\textwidth}
\vspace{-25pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Absolute Effect}  \\ \hline
	  O     & 2.246\\ \hline
	  O:T    &0.454 \\ \hline
	  O:FT:T &0.453 \\ \hline
	  T      &0.451 \\ \hline
	  FT:T   &0.450 \\ \hline
	  O:FT   &0.124 \\ \hline
	  FT     &0.118 \\ \hline
    \end{tabular}
\caption{Table of effects for the three factor experiment}\label{3factorEffect}
\vspace{-25pt}
\end{wraptable}

@@

\begin{wraptable}{l}{0.4\textwidth}
\vspace{-25pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Absolute Effect}  \\ \hline
      O & 58.17 \\ \hline
      E:FC & 45.69 \\ \hline
      O:E:FC & 45.55\\ \hline
      FC & 38.61\\ \hline
      O:FC & 38.56\\ \hline
      O:E & 35.40\\ \hline
      E & 35.38\\ \hline
      O:T & 33.12\\ \hline
      T & 33.12\\ \hline
      O:T:E:FC & 29.31\\ \hline
      T:E:FC & 29.30\\ \hline
      O:T:FC & 28.24\\ \hline
      T:FC & 28.23\\ \hline
      O:T:E & 25.31\\ \hline
      T:E & 25.30\\ \hline
      WT:E & 11.92\\ \hline
      O:WT:E & 11.89\\ \hline
      O:WT:FC & 11.72\\ \hline
      WT:FC & 11.71\\ \hline
      O:D:E & 10.12\\ \hline
    \end{tabular}
\caption{The top twenty significant effects of the ten factor graph}\label{10factorEffect}
      \vspace{-25pt}
\end{wraptable}

>>>>

\begin{wraptable}{l}{0.25\textwidth}
%\vspace{-25pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Effect}  \\ \hline
	  O     & 2.246\\ \hline
	  O:T    &0.454 \\ \hline
	  O:FT:T &0.453 \\ \hline
	  T      &0.451 \\ \hline
	  FT:T   &0.450 \\ \hline
	  O:FT   &0.124 \\ \hline
	  FT     &0.118 \\ \hline
    \end{tabular}
\caption{Table of absolute effects for the three factor experiment}\label{3factorEffect}
%\vspace{-25pt}
\end{wraptable}

@@

\begin{wraptable}{l}{0.25\textwidth}
\vspace{-25pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Effect}  \\ \hline
      O & 58.17 \\ \hline
      E:FC & 45.69 \\ \hline
      O:E:FC & 45.55\\ \hline
      FC & 38.61\\ \hline
      O:FC & 38.56\\ \hline
      O:E & 35.40\\ \hline
      E & 35.38\\ \hline
      O:T & 33.12\\ \hline
      T & 33.12\\ \hline
      O:T:E:FC & 29.31\\ \hline
      T:E:FC & 29.30\\ \hline
      O:T:FC & 28.24\\ \hline
      T:FC & 28.23\\ \hline
      O:T:E & 25.31\\ \hline
      T:E & 25.30\\ \hline
      WT:E & 11.92\\ \hline
      O:WT:E & 11.89\\ \hline
      O:WT:FC & 11.72\\ \hline
      WT:FC & 11.71\\ \hline
      O:D:E & 10.12\\ \hline
    \end{tabular}
\caption{The top twenty significant absolute effects of the ten factor graph}\label{10factorEffect}
      \vspace{-25pt}
\end{wraptable}
